%-------------------------
% Resume in Latex
% Author : Akshay Kalucha
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{hyphenat}
\usepackage{graphicx}
\usepackage{multicol}     %% Allows to create more than two columns
\usepackage{array}        %% For adjusting column widths
\usepackage{fontawesome}
\input{glyphtounicode}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands


\newcommand{\externalLink}{%
  \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
      \begin{scope}[x=1ex, y=1ex]
          \clip (-0.1,-0.1) 
              --++ (-0, 1.2) 
              --++ (0.6, 0) 
              --++ (0, -0.6) 
              --++ (0.6, 0) 
              --++ (0, -1);
          \path[draw, 
              line width = 0.5, 
              rounded corners=0.5] 
              (0,0) rectangle (1,1);
      \end{scope}
      \path[draw, line width = 0.5] (0.5, 0.5) 
          -- (1, 1);
      \path[draw, line width = 0.5] (0.6, 1) 
          -- (1, 1) -- (1, 0.6);
      }
  }

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


% command for projects item
\newcommand{\projectsItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{-1pt}
      \textbf{\small#1} & \small#2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small#2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSkillItem}[2]{
	\item\small{
		\textbf{#1}{#2 \vspace{-2pt}}
	}
}

% \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeProjectSubItem}[2]{\projectsItem{#1}{#2}\vspace{-4pt}}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItem}[2]{\resumeSkillItem{#1}{#2}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{minipage}[t]{\textwidth}
  {\Huge\textbf{\sc Akshay Kalucha}}
  \hfill
  akalucha@hawk.iit.edu \faEnvelope
  
  
  Software Engineer
  \hfill
  \href{https://akcosh.vercel.app}{https://akcosh.me \faHome}\\
  
  Expert in Mobile application development
  \hfill
  \href{https://github.com/akshaykalucha}{akshay \faGithub} \textbar \
  \href{https://www.linkedin.com/in/akshaykalucha/}{akshay \faLinkedin} \\
  
  Chicago, IL
  \hfill
  +13128749117 \faMobile \\
  \end{minipage}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Illinois Institute of Technology}{Chicago, IL}
      {Masters of Science in Information Technology}{Anticipated Graduation: Nov 2024}
      \resumeItemListStart
        \resumeItem{\scriptsize{\footnotesize{\textbf{Concentration:}
        \textit{Software Engineering}
      }}}
      \resumeItemListEnd
      
    \resumeSubheading
    {University of Delhi}{New Delhi, India}
      {Bachelor of Science in Computer Science (Ist Division)}{Jun 2018 -- Aug 2021}
      \resumeItemListStart
        \resumeItem{\scriptsize{\footnotesize{\textbf{Concentrations:}
        \textit{Physical Science, (Mathematics \& Computing)}
        \vspace{-4pt}
        \resumeItem{\scriptsize{\footnotesize{\textbf{Courses:}
        \textit{Calculus and Geometry, Android Programming, Design \& Analysis of Algorithms, Data Structures, Object-Oriented Programming, Computer System Architecture, Probability \& Statistics, Linear Algebra}
        }}}
      }}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {\href{https://www.hypd.store}{HYPD Store}}{New Delhi}
      {Software Engineer}{Dec 2021 - Aug 2022}
      \resumeItemListStart
        \resumeItem{Used Core Data for persistent storage, reducing redundant network requests.}
        \resumeItem{Designed p2p data-channel using webRTC for video streaming, scaling it paralley to run encoding, caching and validation.}
        \resumeItem{Worked with backend engineers to develop server-driven UI in SwiftUI for \href{https://apps.apple.com/in/app/hypd/id1560284106}{hypd store}.}
        \resumeItem{Overhauled software architecture in MVVM, ustilising async/await and concurrency to reduce memory leaks which significantly improved the on-screen time by 40\%.}
        \resumeItem{Implemented Push-Notifications, Deep-Linking and in-app notifications.}
      \resumeItemListEnd
      


\resumeSubheading
{\href{https://www.du.ac.in}{Dept. of Mathematics, University of Delhi}}{New Delhi}
  {Research Intern, Guide Prof: Dr. Umesh Kumar}{Nov 2020 - Jan 2021}
  \resumeItemListStart
    \resumeItem{Implemented a model that applies multinomial naive bayes classification on a comprehensive labelled dataset of around 240k Twitter users to predict the probability of them not being COVID’19 vaccinated.}
    \resumeItem{After model training, we identified an optimal classification threshold, based on F1 score on validation set. The model was then evaluated to achieve reasonable scores.}
  \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.linkedin.com/company/solveclassesapp/}{Intellify}}{New Delhi}
      {Software Developer Intern}{fall 2019 and winter 2020}
      \resumeItemListStart
        \resumeItem{115 Prs Merged, 550 Contributions.}
        \resumeItem{Wrote 6000+ lines of code, released 3 major features.}
        \resumeItem{Designed MVC architecture for the web app and built OTP based login system, JWT Auth, sessions, and Push-Notifications for android app users.}
        \resumeItem{Fixed lots of bugs, resolved lots of jira tickets and sentry issues.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectSubItem{WireBase}
      {A real-time Node.js editor that generates and displays code in readable form}
    \resumeProjectSubItem{Pictureskew}
      {Open-source human-computer emotion detection platform for research to smartfy Indian general stores}
    \resumeProjectSubItem{IIT Stream}
      {Multi-client video lecture streaming platform for IIT students}
    \resumeProjectSubItem{PyCalc}
      {Neural network package to solve ordinary and partial equations}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\resumeProjectSubItem{Proficient}
{Javascript, Swift, Java, Python}
\resumeProjectSubItem{Mobile}
{SwiftUI, UIKit, Kotlin, React-Native, Cocoa Touch, Objective-C}
\resumeProjectSubItem{Web}
{React, Express, Node, Nextjs}
\resumeProjectSubItem{Utilities}
{Shell Utilities, Git, PostgreSQL, MongoDB, Firebase, LaTeX}
\resumeSubHeadingListEnd

%--------Extracurricular------------
\section{Extracurricular}
\textbf{} \\\hspace{3mm} Expoited and patched the zoobar server as part of Computer Systems Security Course.
\textbf{} \\\hspace{3mm} Developed iOS app in swiftUI which was a Websocket Client for a Websocket Server hosting multiplayer game.
\textbf{} \\\hspace{3mm} Awarded the graduate pathway scholarship by college of computing at Illinois Institute of Technology, 2022.
\textbf{} \\\hspace{3mm} Mentored Code for Safe India hackathon at Indian Institute of Technology, Delhi, 2020.


%-------------------------------------------
\end{document}
